Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added PTSD positive diagnosis by sample chunk
Added control positive by sample chunk

>>>>

```{r Get PTSD positive by sample}

dat.retro_PTSD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)

dat.retro_PTSD_by_sample <- dat.retro_PTSD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("PTSD" = n())

```{r Get control positive by sample}

dat.retro_control_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(control_numeric) %>% 
  filter(control_numeric == 1)

dat.retro_control_by_sample <- dat.retro_control_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("No diagnosis" = n())
